Liveness-Based Garbage Collection for Lazy Languages

### 2015-11-28 paper/paper.tex

%\comment{  
Consider  the program in  Figure~\ref{fig:mot-example2}.  As
  mentioned earlier,  a lazy  evaluation of  the $\LET$  expression at
  $\pi_1$ creates a closure for $(length~x)$ instead of evaluating it.
  Since the  closure may escape the  scope in which it  is created, it
  carries a copy  of $x$ within itself.   We treat the copy  of $x$ in
  the closure as being separate from the $x$ introduced by the $\LET$,
  and call  it a \emph{closure variable}.   For liveness calculations,
  such variables are distinguished from variables introduced by \LET s
  and  function arguments  (called \emph{stack  variables} since  they
  reside in the activation stack). Notationally, we distinguish
  closure variables from their corresponding stack variables by
  subscripting them with their program points of
  creation.\footnote{Mutiple occurrences of the same variable in an
    application are further distinguished by their positions in the
    application.}

>>>>

%\comment{  
Consider  the program in  Figure~\ref{fig:mot-example2}.  As
  mentioned earlier,  a lazy  evaluation of  the $\LET$  expression at
  $\pi_1$ creates a closure for $(length~x)$ instead of evaluating it.
  Since the  closure may escape the  scope in which it  is created, it
  carries a copy  of $x$ within itself.   We treat the copy  of $x$ in
  the closure as being separate from the $x$ introduced by the $\LET$,
  and call  it a \emph{closure variable}.   For liveness calculations,
  such variables are distinguished from variables introduced by \LET s
  and  function arguments  (called \emph{stack  variables} since  they
  reside in the activation stack). Notationally, we distinguish
  a closure variable from its corresponding stack variable by
  subscripting it with the program point where the closure was created\footnote{Mutiple occurrences of the same variable in an
    application are further distinguished by their positions in the
    application.}.
